\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\begin{document}

@@

>>>>

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$}

\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\hei}{[\ion{He}{1}]} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\siii}{[\ion{S}{3}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\neiii}{[\ion{Ne}{3}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\newcommand{\znii}{\ion{Zn}{2}} 
\newcommand{\crii}{\ion{Cr}{2}} 
\newcommand{\mnii}{\ion{Mn}{2}} 
\newcommand{\tiii}{\ion{Ti}{2}} 
\newcommand{\caii}{\ion{Ca}{2}}

\begin{document}

@@

	\subsection{GRB100316D (z = 0.059)}
	The data presented here also formed the basis of GCN \#
	10512\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10512.gcn3}}, GCN \#
	10513\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10513.gcn3}}, GCN \#
	10543\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10543.gcn3}} and is published in \citet{Bufano2012} and \citet{Starling2011}. This GRB has an associated SN and has therefore undergone intense follow-up. 
	The data presented here consists only of a subset of the entire VLT/X-shooter campaign. The transition from

	\subsection{GRB100418A (z=0.624)}
	The data presented here also formed the basis of GCN \#
	10620\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10620.gcn3}} and GCN \#
	10631\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10631.gcn3}} and is published
	in \citet{DeUgartePostigo2011}.
	The burst have been followed up in three epochs of observations, 0.4, 1.4, and
	2.4 days after the burst, each lasting 4.8 ks.
	The unambiguous redshift of the host, $z=0.624$, is found from the simultaneous detection of emission features belonging to nebular lines, including \hi, \oii, \oiii, \neiii, \nii, \sii, \siii, and \hei~as well as absorption features due to the presence of \znii, \crii, \feii, \mnii, \mgii, \mgi, \tiii, and \caii, all at a consistent redshift. 
	Temporal evolution of the fine-structure lines belonging to \feii$^*$ is found between the epochs.
